\begin{tikzpicture}[scale=1.0]
    \clip (0,0) rectangle (\paperwidth,\paperheight);
    \fill[color=cwrugray] (\framespacing,\framespacing) rectangle (\paperwidth-\framespacing,\framespacing+\framethickness);
    \fill[color=cwrugray] (\paperwidth-\framespacing,\framespacing) rectangle (\paperwidth-\framespacing-\framethickness,\textheight-\framespacing);
    \fill[color=cwrugray] (\framespacing,\framespacing) rectangle (\framespacing+\framethickness,\textheight-\framespacing);
    \fill[color=cwrugray] (\framespacing,\textheight-\framespacing) rectangle (\paperwidth-\framespacing,\textheight-\framespacing-\framethickness);

\hop{1.0}{1.0}{Admiral}{11--15\%}{Said to be citrus, orange flavored. A good compliment hop to Targets. Good dual purpose hop.}{English IPAs, Ales}{All Purpose}{US}
\hop{1.0}{4.5}{Anthanum}{3.5--6\%}{This hop is used for its aromatic properties and moderate bittering. It has aromas that are citrus (Grapefruit), earthy, and floral.}{American Ales}{All Purpose}{US}
\hop{1.0}{8.0}{Amarillo}{8--10\%}{Popular American mid-range alpha acid variety with a unique and distinct aroma. It has a flowery, citrus-like aroma; more orange than grapefruit.}{Pale Ales, IPAs, Porters}{All Purpose}{US}
\hop{1.0}{11.5}{Apollo}{18--21\%}{Characterized by its exceptionally high percentage of Alpha Acids, it has excellent storage stability. It has citrus notes, with emphasis on orange. It is resiny, and spicy.}{Big Hop Profile Beers}{All Purpose}{US}
\hop{1.0}{15.0}{Aquila}{6--7.5\%}{Recently developed as an aroma hop originating in the US.}{American Ales}{All Purpose}{US}
\hop{1.0}{18.5}{Banner}{9--11\%}{Similar to Aquila and Cluster with good yield.}{American Lagers}{All Purpose}{US}
\hop{1.0}{22.0}{Bramling Cross}{5--8\%}{Variety Bramling crossed with a male seedling from a Manitoba female. Blackcurrant, lemony aroma.}{Spiced Ales}{All Purpose}{US}
\hop{1.0}{25.5}{Bravo}{14--17\%}{New Super High Alpha. The higher Co-Ho levels mean a not completely smooth bittering, but not as harsh as Chinook. (Its bittering properties are similar to Simcoe). Flavor and aroma are described as an earthy spice and herb, fruity and floral, so, I guess that it is different things to different people. It's a descendant of Zeus and Nugget.}{American IPAs, American Pale Ales, American Stouts}{All Purpose}{US}
\hop{1.0}{29.0}{Brewer's Gold}{6--9\%}{Sibling of and similar to Bullion only maturing earlier and more disease resistant. English/wild Canadian cross. Pungent English character.}{Stouts, Dark Ales}{All Purpose}{US}
\hop{6.5}{1.0}{Bullion}{6.5--9\%}{Intense, black currant aroma, spicy and pungent. One of the earliest high alpha hops in the world. Raised in 1919 in England from a wild Manitoban female crossed with an English male hop.}{Stouts, Dark Ales}{All Purpose}{US}
\hop{6.5}{4.5}{Calypso}{10--12\%}{Pleasant, fruity aroma, with hints of pear and apple.}{Ales, Stouts, Barley Wines}{All Purpose}{US}
\hop{6.5}{8.0}{Cascade}{4--7\%}{Flowery, citrus, and spice with grapefruit the noticeable fragrance quite often. This medium aroma balances the low bittering value. Derived from a cross between Fuggles and the Russian hop Serebrianker. Very popular hop among craft brewers. Good for flavor and aroma, but an acceptable bittering hop.}{Pale Ales, IPAs, Porters}{All Purpose}{US}
\hop{6.5}{11.5}{Centennial}{9--11\%}{Flowers and citrus most evident. A medium aroma with mid-to-high bittering value makes it a dual purpose choice. Cross between Brewer's Gold and a selected USDA male.}{Medium American Ales, Dark American Ales}{All Purpose}{US}
\hop{6.5}{15.0}{Challenger}{7--10\%}{Mild to Moderate aroma, quite spicy. One of the few recognized all-purpose hops combining moderate amounts of alpha acid with a good kettle aroma.}{British Ales, British Lagers}{All Purpose}{US}
\hop{6.5}{18.5}{Chinook}{11--13\%}{Mild to medium-heavy, spicy, distinct piney aroma like a pine forest washed with exotic spice and infused with grapefruit. This alluring aroma and a high bittering value has gained this hop full respect from craft and major brewers. Cross between Petham Golding and USDA select male.}{Pale Ales, Lagers}{All Purpose}{US}
\hop{6.5}{22.0}{Citra}{10--11\%}{Very fruity citrus, peach, apricot, passion fruit, grapefruit, lime, melon, gooseberry, lychee fruit, pineapple, mango, papaya and other tropical fruit flavors and aromas. A very new high alpha Hallertauer Mittelfruh, Tettnanger, EKG hybrid with distinctive citrus aroma.}{Pale Ales, IPAs}{All Purpose}{US}
\hop{6.5}{25.5}{Cluster}{5.5--8.5\%}{Floral aroma, excellent general-purpose hop with medium and well-balanced bittering potential and no undesirable aroma properties. Good for Dark beers.}{American Lagers}{All Purpose}{US}
\hop{6.5}{29.0}{Columbia}{12--16\%}{A Centennial substitute. Very pungent, aromatic, and clean tasting.}{Ambers, Pale Ales, Porters, Stouts}{All Purpose}{US}
\hop{12.0}{1.0}{Columbus}{13--16\%}{Earthy, spicy, pungent, with some citrus overtones. Not overwhelmingly citrus like Cascade. High on the bittering scale yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal, surprisingly pleasant aroma.}{Pale Ales, American IPAs, Stouts, Lagers}{All Purpose}{US}
\hop{12.0}{4.5}{Comet}{8--11\%}{A rare US hop. Used primarily for their bittering character. Wild American aroma that is objectionable to some brewers, Comet today is no longer grown commercially.}{Ales, Lagers}{All Purpose}{US}
\hop{12.0}{8.0}{Crystal}{3--5\%}{Mild and pleasant, a delicate blend of spices and flowers. Low bittering value adds to the charm. Known as a triploid, three hops contributing characteristics: Cascade, Brewer's Gold and Early Green.}{German-style Pilsners, Lagers, Koelsch, ESB, Belgian Ales}{All Purpose}{US}
\hop{12.0}{11.5}{Delta}{6.5\%}{Aroma Type Hop Mild and pleasant, slightly spicy with a hint of citrus. Still experimental.}{American Pale Ales, American IPAs}{All Purpose}{US}
\hop{12.0}{15.0}{Eroica}{11--13\%}{Aroma is quite strong, but not unpleasant. Better aroma than many high alpha acid hops. Suitable for general bittering. Bred by open pollination of Brewer's Gold.}{Pale Ales, Dark Ales, Stouts}{All Purpose}{US}
\hop{12.0}{18.5}{First Gold}{6--9\%}{Pleasant citrus/apricot nose that is outstanding in ESBs, IPAs, or fruit beers. Dwarf hop with fine English Golding character with higher alpha.}{English Ales, Porters, ESBs, Fruit Beers}{All Purpose}{US}
\hop{12.0}{22.0}{Fuggle}{4--5.5\%}{Classic English aroma hop with moderate bittering value. Mild and pleasant, spicy, soft, woody, with some fruit tones. Also known over-seas as Styrian Golding.}{English Ales, Pale Ales, Porters, Stouts}{All Purpose}{US}
\hop{12.0}{25.5}{Galaxy}{11--13\%}{Australian high alpha dual purpose hop with a big unique aroma, described as a combination of citrus and passionfruit. Used in Widmer Galaxy Hopped Barley Wine.}{Pale Ales, IPAs, Barley Wines}{All Purpose}{US}
\hop{12.0}{29.0}{Galena}{10--12\%}{Medium aroma but pleasant hoppiness. Bred from Brewer's Gold by open pollination. Excellent high alpha acid hop with balanced bittering profiles paired with acceptable hop aroma.}{American Ales, American Stouts, American Lagers}{All Purpose}{US}
\hop{17.5}{1.0}{Glacier}{5--6\%}{Pleasant aroma of citrus mixed with sweet fruity of pear or apricot. Aroma seems to be the strong suit of this hop.}{American Ales, ESBs}{All Purpose}{US}
\hop{17.5}{4.5}{Golding}{4--5\%}{Refined Gentle, Fragrant and pleasant with flowery tones, that has produced some of England's best bitters.}{English Ales, Belgian Ales}{All Purpose}{US}
\hop{17.5}{8.0}{Green Bullet}{9--11\%}{A high alpha hop with fruity and resiny flavors and floral aromas, from New Zealand. Considered a bittering variety typically for lagers, Green Bullet also carries a solid Styrian characteristic of subtle spiciness which finds it at home in a freshly drawn pint of Bitter or an Irish-style Dry Stout.}{Lagers}{All Purpose}{US}
\hop{17.5}{11.5}{Domestic Hallertau}{5--6\%}{Named for its origins in the Hallertauer region of Germany, this is a noble aroma hop with ever-so-subtle flower and spice fragrances defining its ``"{u}ber alles'' superiority.}{Stock Ales, Altbiers, Belgian Ales, Continental Lagers, Pilsners, Bocks, Lagers, Wheats}{All Purpose}{US}
\hop{17.5}{15.0}{German Hallertau}{3.5--5\%}{Traditionally a superior German aroma hop. Mild to semi-strong aroma, the most popular variety. Excellent flavor.}{Wheats, Altbiers, Pilsners, Belgian Ales, American Lagers, German Lagers}{All Purpose}{US}
\hop{17.5}{18.5}{Hersbrucker Hallertau}{3--5\%}{Drier, spicier than Hallertauer. Most important aroma variety in Germany.}{German Ales, German Lagers}{All Purpose}{US}
\hop{17.5}{22.0}{Mittelfr\"{u}h Hallertau}{3--5\%}{Typical characteristics of a Hallertau; mild and pleasant aroma.}{Stock Ales, Altbiers, Belgian Ales, Continental Lagers, Pilsners, Bocks, Lagers, Wheats}{All Purpose}{US}
\hop{17.5}{25.5}{Herald}{11--13\%}{New high-alpha acid dwarf hop.}{}{All Purpose}{US}
\hop{17.5}{29.0}{Horizon}{12--14\%}{A cross between Brewers gold and German (probably Hallertau) aroma hops bred in Oregon.}{American Ales, American Lagers}{All Purpose}{US}
\hop{23.0}{1.0}{Huller}{4--6\%}{A universal hop for both bittering and aroma.}{German Ales, German Lagers}{All Purpose}{US}
\hop{23.0}{4.5}{Kent Golding}{3--5\%}{Refined gentle, fragrant and pleasant with flowery tones. Traditional old English hop. Referred to as East Kent Goldings if grown in East Kent, Kent Goldings if grown in Mid-Kent, and Goldings if grown elsewhere.}{English Ales, Belgian Ales}{All Purpose}{US}
\hop{23.0}{8.0}{Liberty}{3--5\%}{American cousin to Hallertau with very similar flower and spice characteristics, mild and pleasant, quite fine. Best used as a finishing hop in German-style lagers.}{American Ales, German Ales, Lagers, Pilsners, Bocks, Koelsch}{All Purpose}{US}
\hop{23.0}{11.5}{Lublin}{3--4.5\%}{Mild and typical of noble aroma types. Another source of the classical noble- aroma type hop with long and strong traditions. Widely believed to be a clone of Saaz.}{}{All Purpose}{US}
\hop{23.0}{15.0}{Magnum}{12--17\%}{A German thoroughbred with limited Pacific Northwest plantings. Prized for its high bittering value, the aromatic nature is one of spice and citrus, but is minimal compared to its big bittering.}{Pale Ales, IPAs, German Lagers}{All Purpose}{US}
\hop{23.0}{18.5}{Millenium}{14--16\%}{Very similar to Nugget hops in aroma and flavor. Some descriptors included floral, resiny, and a bit spicy/herbal.}{American Ales}{All Purpose}{US}
\hop{23.0}{22.0}{Motueka}{6.5--7.5\%}{An excellent hop in many applications from first kettle additions through to late. This hop offers a unique aroma and flavour making it suitable for producing bigger more traditional style Lagers, especially Bohemian Pilsner. Excellent when employed in multiple additions from a single hop bill and sits well on the palate to balance speciality malt sweetness. An excellent variety for Belgian Ales and gives a real edge to Cask Bitter.}{Belgian Ales}{All Purpose}{US}
\hop{23.0}{25.5}{Mt.\ Hood}{5--8\%}{Hybrid of Hallertau with similar mild flower/spice aroma characteristics with a hint more of the forest. ``Clean'' commonly describes it, with similarities to the German Hallertau and Hersbrucker varieties.}{American Ales, American Lagers, German Ales, German Lagers}{All Purpose}{US}
\hop{23.0}{29.0}{Nelson Sauvin}{12--13\%}{Described to have a white wine fruitiness of ``crushed gooseberries.'' A hop that requires judicious application in the brew house, this truly unique dual-purpose variety can be used to produce big punchy Ales as well as subtle yet bitter Lagers. The fruitiness may be a little overpowering for the uninitiated, however those with a penchant for bold hop character will find several applications for this true brewer's hop.}{Ales, Lagers}{All Purpose}{US}
\hop{28.5}{1.0}{Newport}{10--17\%}{Mild aroma. Fairly pungent, resiny flavor. An Oregon original derived from Brewers gold, Mittelfruh, Late Grape, Belgium 31, and Fuggle. Newport hops were bred as a potential replacement to Galena based on their resistance to mildew. Widely used by the Rogue Brewery.}{}{All Purpose}{US}
\hop{28.5}{4.5}{New Zealand Hallertau}{8--9\%}{Bred from the German Hallertau Mittelfruh, this aroma hop is characterized by woodsy, citrus notes and a clean taste that has staying power. Higher alpha makes it an acceptable bittering hop as well.}{Organic Pilsners, Lagers, German Beers}{All Purpose}{US}
\hop{28.5}{8.0}{Northdown}{7--10\%}{Mellow English higher alpha-acid hop. Similar to Northern Brewer, but with a better flavor and aroma than domestic Northern Brewer; A clean bittering hop.}{Heavier Ales, Porters}{All Purpose}{US}
\hop{28.5}{11.5}{Northern Brewer}{7--11\%}{A true dual-purpose hop containing moderate amounts of alpha acids combined with an acceptable aroma profile. Neutral, clean aroma, woody with evergreen and mint overtones and slightly higher-than-average bittering value.}{English Ales, ESBs, Bitters, Porters, German Lagers, Steam Beers}{All Purpose}{US}
\hop{28.5}{15.0}{Nugget}{11--16\%}{Strong heavy and herbal, spicy aroma and high bittering value (along with desirable growing traits) has brought this hop variety to the forefront of the industry. Selected from a cross between Brewer's Gold and a high alpha male.}{Ales, Stouts}{All Purpose}{US}
\hop{28.5}{18.5}{Olympic}{11--13\%}{Moderate aroma. Similar to Chinook and Brewers Gold.}{Dark Ales, Stouts}{All Purpose}{US}
\hop{28.5}{22.0}{Omega}{9--11\%}{A very new very bitter hop.}{Ales, Stouts, Lagers}{All Purpose}{US}
\hop{28.5}{25.5}{Orion}{6--8\%}{Classic Noble style, dual-use hop from Germany.}{German Ales, German Lagers}{All Purpose}{US}
\hop{28.5}{29.0}{Pacifica}{5--6\%}{The Pacifica brings something of a blend of new and old-world taste descriptors to the brewers' forum. Orange marmalade aptly describes the citrus aroma notes achieved through late addition. Bittering quality is such that early kettle additions net a soft yet solid finish even in highly bittered beers.}{}{All Purpose}{US}
\hop{34.0}{1.0}{Pacific Gem}{15--17\%}{A pleasing fruity aroma of blackberries with a woodsy flavor are the essence of this variety used mainly as a bittering agent in organic beers.}{Organic Pale Ales, IPAs}{All Purpose}{US}
\hop{34.0}{4.5}{Pacific Jade}{12--14\%}{The aroma of this hop is described as ``bold'' as it delivers a herbal infusion of fresh citrus and crushed black pepper. The citrus aroma and flavour notes work well to temper malt sweetness in ``fullish'' Ales especially when used moderately as a finishing hop.}{Dry Lagers}{All Purpose}{US}
\hop{34.0}{8.0}{Palisade}{6--9\%}{Aroma described as floral, Subtle Apricot, Grassy or ``Pretty.'' Non-aggressive, smooth hop flavor with a fruity, non-citrus aroma more characteristic of English style Pale ales.}{English Ales}{All Purpose}{US}
\hop{34.0}{11.5}{Perle}{7--9\%}{A palate-pleaser with its moderate, pleasant, minty clean bittering qualities and refreshing, spicy ``green hop'' aroma. Derived from English Northern Brewer.}{Pale Ales, Lagers, Stouts}{All Purpose}{US}
\hop{34.0}{15.0}{Phoenix}{10--12\%}{Attractive English aroma (sources say similar to challenger) with high alpha- acid. Use as an aroma hop were reportedly disappointing.}{English Ales, Porters, Stouts, ESBs, Bitters}{All Purpose}{US}
\hop{34.0}{18.5}{Pioneer}{8--10\%}{New dwarf variety with clean bitterness and mild English aroma. Unusual pleasant lemon/grapefruit citrus aroma distinctively hoppy.}{English Ales, ESBs, Bitters}{All Purpose}{US}
\hop{34.0}{22.0}{Pride of Ringwood}{7--10\%}{Quite pronounced aroma but not unpleasant, citrus-like. At the time of release in 1965 it was the highest alpha hop in the world. closely associated with such famous beers as Foster's Lager.}{British Ales, Australian Ales, Australian Lagers}{All Purpose}{US}
\hop{34.0}{25.5}{Progress}{5--8\%}{Similar to Fuggles but a little sweeter. Also known as UK Progress and Wye Progress. Bred from Whitbred Goldings Vareity but with an assertive fruity aroma. Robust, Fruity, with Lime. M. Jackson called them ``junipery.''}{Cask Ales, English Ales, Scottish Ales}{All Purpose}{US}
\hop{34.0}{29.0}{Riwaka}{4.5--6.5\%}{Powerful grapefruit ``citrus'' characters are literally breathtaking. A punchy addition to the new-world styles of Pale Ale and regional Pilsners. A cult hero that is established in the New Zealand craft beer culture.}{Pale Ales}{All Purpose}{US}
\hop{39.5}{1.0}{Saaz}{3--5\%}{The Old World steadfast standby made famous by Pilsner Urquell possesses the aromatic blend of earth and spice notable in European nobles. Low bittering value.}{Continental Lagers, Wheats, Pilsners, Lagers}{All Purpose}{US}
\hop{39.5}{4.5}{Santiam}{5.5--8\%}{Resembles a Noble hop aroma. Herbal. Floral. This is a mixture of Tettnanger, Mittelfruh, Cascades, and who knows what else. Aroma is a suggestion of Tettnanger. Another product of Corvallis Oregon.}{American Lagers, German Lagers, German Ales, Wheats}{All Purpose}{US}
\hop{39.5}{8.0}{Saphir}{3--4.5\%}{Refined, sweet, mild clean citrus, hint of tangerine. It was bred with a Hallertau parent and probably a long list of other hops to make it more commercially viable.}{Pilsners, German Lagers, Belgian Whites}{All Purpose}{US}
\hop{39.5}{11.5}{Simcoe}{12--14\%}{Aromas of passionfruit, apricot, intense pine and woodsy aroma adds to the fresh, youthful vigor of this complex hop. Dual purpose but generally considered a bittering hop.}{American Ales, IPAs, Double IPAs}{All Purpose}{US}
\hop{39.5}{15.0}{Sladek}{9--10\%}{Hybrid aroma variety of Saaz type with excellent impact on hoppy taste and aroma of beer. New dual purpose Czech hop.}{Lagers}{All Purpose}{US}
\hop{39.5}{18.5}{Sorachi Ace}{13--16\%}{A Japanese winner by all counts with its powerful lemon aroma, high bittering value and flavorful personality.}{American Ales, Lagers, Pale Ales, Wheats}{All Purpose}{US}
\hop{39.5}{22.0}{Southern Cross}{12\%}{The aroma is characterized by a heady mix of lemon peel and pine needles layered beneath the clean spiciness. Primarily a bittering hop but reported to have a nice mellow aroma as a late addition hop.}{Australian Lagers}{All Purpose}{US}
\hop{39.5}{25.5}{Spalter}{3--6\%}{Traditional German noble hop. A Saaz alternative, aromatic and flavorful.}{German Lagers}{All Purpose}{US}
\hop{39.5}{29.0}{Sterling}{6--9\%}{Herbs and spices dominate, flowers and citrus around the fringes. Moderate bittering values with a mix of Saaz and Mt. Hood properties.}{Ales, Pilsners, Lagers}{All Purpose}{US}
\hop{45.0}{1.0}{Sticklebract}{9--11\%}{Noted for its piney, citrus aroma. May give a unique New Zealand twist to English beer styles. Coarse, high-alpha acid variety.}{Ales}{All Purpose}{US}
\hop{45.0}{4.5}{Styrian Goldings}{4--6\%}{Delicate, slightly spicy, soft and floral. A world renowned aroma hop with widespread usage in both ale and lager brewing. An ecotype of Fuggle grown in Slovenia.}{English Ales, Oktoberfest Lagers, Belgian Ales, Pilsners}{All Purpose}{US}
\hop{45.0}{8.0}{Summit}{17.5--19.5\%}{Quite new on the scene (2003) but the consensus is very positive with its ``peak'' bittering value coupled with robust citrus notes of orange, tangerine and grapefruit. Receiving accolades as an ideal hop for the ultimate Pale Ale.}{Pale Ales, IPAs}{All Purpose}{US}
\hop{45.0}{11.5}{Sun}{15--16\%}{A super alpha hop. Not much info on this one.}{}{All Purpose}{US}
\hop{45.0}{15.0}{Super Alpha}{10--12\%}{Slight fresh grassiness beneath a mix of aromas such as pine needles and lemongrass. A very versatile hop in the brew house where it can be used to deliver a very crisp bitter edge on the back pallet as well as excellent aroma qualities. Like most New Zealand varieties the exceptional oil profile sets it apart as a hop with many applications.}{}{All Purpose}{US}
\hop{45.0}{18.5}{Super Galena}{13--16\%}{Super Galena is a super high alpha variety developed by the Hopsteiner breeding program and released in 2006. It has relatively high contents of both alpha and beta acids, making it a good bittering hop with pleasant aroma. Super Galena is comparable to Galena in its aroma and bitterness profile, but offers a substantially higher yield and complete resistance to all current hop powdery mildew strains found in the US.}{American Ales, American Stouts, American Lagers}{All Purpose}{US}
\hop{45.0}{22.0}{Talisman}{7--9\%}{An improved Cluster variety. Not much more info available.}{}{All Purpose}{US}
\hop{45.0}{25.5}{Target}{10--12\%}{Widely used for high alpha acid content combined with an acceptable aroma. Pleasant English hop aroma, quite intense.}{British Ales, British Lagers}{All Purpose}{US}
\hop{45.0}{29.0}{Taurus}{12--15\%}{Ultra high-alpha acid variety of Hallertau, giving medium bitterness. It has a distinctive hoppy tang with a delicate aroma.}{}{All Purpose}{US}
\hop{50.5}{1.0}{Tettnang}{4--5\%}{Fine, very spicy, mild, floral, very aromatic. Recently established in the US, a traditional German variety, true noble aroma variety.}{Wheats, Lagers}{All Purpose}{US}
\hop{50.5}{4.5}{Tomahawk}{14--17\%}{Earthy, spicy, pungent, with some citrus overtones. Not overwhelmingly citrus like Cascade. High on the bittering scale yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal.}{American Ales, Stouts}{All Purpose}{US}
\hop{50.5}{8.0}{Tradition}{10--13\%}{High-alpha acid Hallertau variety with German characteristics grown to replace Hersbrucker.}{Lagers, Pilsners, Bocks, Wheats, Weizens}{All Purpose}{US}
\hop{50.5}{11.5}{Ultra}{3\%}{Newer domestic aroma variety with Saaz characteristics. Very fine, mild, spicy with floral notes. Bred as a substitute for Hallertauer Mittelfruh.}{Pilsners, German Lagers}{All Purpose}{US}
\hop{50.5}{15.0}{Vanguard}{4--6\%}{Slightly flowery, mild. Similar to Hallertau Mittlefruh and saaz in aroma. A gentle hop for subtle bitterness, aroma, and flavor.}{Light Lagers, Pilsners, Kolsch, Wheat, Munich Helles}{All Purpose}{US}
\hop{50.5}{18.5}{Warrior}{14.5--17\%}{Grapefruity and lemony, some piney notes. Also saw pineapple as a descriptor. Its high bittering value and very mild aroma offers new dimensions to IPA and Double IPA brewers.}{IPAs}{All Purpose}{US}
\hop{50.5}{22.0}{Willamette}{4--6\%}{The king of aroma hops in the US with its modest bittering value and the joyous harmony of flowers, fruit, earth and spice. A quality aroma hop with a smooth soft flavor.}{American Ales, American Lagers, British Ales, British Lagers}{All Purpose}{US}
\hop{50.5}{25.5}{Yeoman}{9--14\%}{A popular bittering hop in the UK. Similar to Targets. Not too available in the US.}{British Ales, British Lagers}{All Purpose}{US}
\hop{50.5}{29.0}{Zenith}{9--10\%}{Has a good aroma. Not too available.}{British Ales, British Lagers}{All Purpose}{US}
\hop{56.0}{1.0}{Zeus}{14--17\%}{Earthy, spicy, pungent, with some citrus overtones. Not overwhelmingly citrus like Cascade. High on the bittering scale yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal.}{American Ales, American Stouts}{All Purpose}{US}

\end{tikzpicture}
