\hop{1.5}{1.5}{Apollo}{18--21\%}{Characterized by its exceptionally high percentage of Alpha Acids, it has excellent storage stability. It has citrus notes, with emphasis on orange. It is resiny, and spicy.}{Big~Hop~Profile~Beers}{Bittering}{US}
\hop{6.0}{1.5}{Bravo}{14--17\%}{Not completely smooth bittering, but not as harsh as Chinook (similar to Simcoe). Flavor and aroma are described as an earthy spice and herb, fruity and floral.}{American~IPAs, American~Pale~Ales, American~Stouts}{Bittering}{US}
\hop{10.5}{1.5}{Columbus}{13--16\%}{Earthy, spicy, pungent, with some citrus overtones. High bittering yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal, surprisingly pleasant aroma.}{Pale~Ales, IPAs, Stouts, Lagers}{All Purpose}{}
\hop{15.0}{1.5}{Magnum}{12--17\%}{A German thoroughbred with limited Pacific Northwest plantings. Prized for its high bittering value, the aromatic nature is one of spice and citrus, but is minimal compared to its big bittering.}{Pale~Ales, IPAs, German~Lagers}{Bittering}{DE}
\hop{19.5}{1.5}{Millenium}{14--16\%}{Very similar to Nugget hops in aroma and flavor. Some descriptors included floral, resiny, and a bit spicy/herbal.}{American~Ales}{Bittering}{}
\hop{24.0}{1.5}{Pacific Gem}{15--17\%}{A pleasing fruity aroma of blackberries with a woodsy flavor are the essence of this variety used mainly as a bittering agent in organic beers.}{Organic~Pale~Ales, IPAs}{Bittering}{NZ}
\hop{28.5}{1.5}{Summit}{17.5--19.5\%}{New since 2003, but a positive consensus with its ``peak'' bittering value coupled with robust citrus notes of orange, tangerine and grapefruit. Receiving accolades as an ideal hop for the ultimate Pale Ale.}{Pale~Ales, IPAs}{Bittering}{}
\hop{33.0}{1.5}{Tomahawk}{14--17\%}{Earthy, spicy, pungent, with some citrus overtones (not overwhelmingly citrus like Cascade). High bittering yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal.}{American~Ales, Stouts}{Bittering}{}
\hop{37.5}{1.5}{Warrior}{14.5--17\%}{Grapefruity and lemony, some piney notes. Also saw pineapple as a descriptor. Its high bittering value and very mild aroma offers new dimensions to IPA and Double IPA brewers.}{IPAs}{Bittering}{}
\hop{42.0}{1.5}{Zeus}{14--17\%}{Earthy, spicy, pungent, with some citrus overtones (not overwhelmingly citrus like Cascade). High bittering yet also valued for its oil content creates a hop that is an interesting dichotomy of sharp and herbal.}{American~Ales, American~Stouts}{Bittering}{}
\hop{1.5}{4.5}{Admiral}{11--15\%}{Said to be citrus, orange flavored. A good compliment hop to Targets. Good dual purpose hop.}{English~IPAs, Ales}{Bittering}{UK}
\hop{6.0}{4.5}{Columbia}{12--16\%}{A Centennial substitute. Very pungent, aromatic, and clean tasting.}{Ambers, Pale~Ales, Porters, Stouts}{Bittering}{}
\hop{10.5}{4.5}{Horizon}{12--14\%}{A cross between Brewers gold and German (probably Hallertau) aroma hops bred in Oregon.}{American~Ales, American~Lagers}{Bittering}{}
\hop{15.0}{4.5}{Newport}{10--17\%}{Mild aroma. Fairly pungent, resiny flavor. An Oregon original derived from Brewers gold, Mittelfr\"{u}h, Late Grape, Belgium 31, and Fuggle. Widely used by the Rogue Brewery.}{}{Bittering}{US}
\hop{19.5}{4.5}{Nugget}{11--16\%}{Strong heavy and herbal, spicy aroma and high bittering value (along with desirable growing traits) has brought this hop variety to the forefront of the industry.}{Ales, Stouts}{All Purpose}{}
\hop{24.0}{4.5}{Pacific Jade}{12--14\%}{The aroma is described as ``bold'' as it delivers a herbal infusion of fresh citrus and crushed black pepper. Works well to temper malt sweetness in ``fullish'' Ales especially as a finishing hop.}{Dry~Lagers}{All Purpose}{NZ}
\hop{28.5}{4.5}{Simcoe}{12--14\%}{Aromas of passionfruit, apricot, intense pine and woodsy aroma adds to the fresh, youthful vigor of this complex hop. Dual purpose but generally considered a bittering hop.}{American~Ales, IPAs, Double~IPAs}{Bittering, Flavor}{}
\hop{33.0}{4.5}{Sorachi Ace}{13--16\%}{A Japanese winner by all counts with its powerful lemon aroma, high bittering value and flavorful personality.}{American~Ales, Lagers, Pale~Ales, Wheats}{Bittering}{JP}
\hop{37.5}{4.5}{Super Galena}{13--16\%}{Super Galena was developed by the Hopsteiner breeding program and released in 2006. It has high contents of both alpha and beta acids, making it a good bittering hop with pleasant aroma.}{American~Ales,~Stouts,~and~Lagers}{Bittering}{}
\hop{42.0}{4.5}{Taurus}{12--15\%}{Ultra high-alpha acid variety of Hallertau, giving medium bitterness. It has a distinctive hoppy tang with a delicate aroma.}{}{Bittering}{}
\hop{1.5}{7.5}{Calypso}{10--12\%}{Pleasant, fruity aroma, with hints of pear and apple.}{Ales, Stouts, Barley~Wines}{Dual Purpose}{}
\hop{6.0}{7.5}{Chinook}{11--13\%}{Mild to medium-heavy, spicy, distinct piney aroma like a pine forest washed with exotic spice and infused with grapefruit.}{Pale~Ales, Lagers}{Bittering}{}
\hop{10.5}{7.5}{Eroica}{11--13\%}{Aroma is quite strong, but not unpleasant. Better aroma than many high alpha acid hops. Suitable for general bittering. Bred by open pollination of Brewer's Gold.}{Pale~Ales, Dark~Ales, Stouts}{All Purpose}{}
\hop{15.0}{7.5}{Galaxy}{11--13\%}{Australian high alpha dual purpose hop with a big unique aroma, described as a combination of citrus and passionfruit. Used in Widmer Galaxy Hopped Barley Wine.}{Pale~Ales, IPAs, Barley~Wines}{All Purpose}{AU}
\hop{19.5}{7.5}{Herald}{11--13\%}{New high-alpha acid dwarf hop.}{}{Bittering}{}
\hop{24.0}{7.5}{Nelson Sauvin}{12--13\%}{Described to have a white wine fruitiness of ``crushed gooseberries.'' A hop that requires judicious application in the brew house; the fruitiness may be a little overpowering for the uninitiated.}{Ales, Lagers}{Bittering}{NZ}
\hop{28.5}{7.5}{Olympic}{11--13\%}{Moderate aroma. Similar to Chinook and Brewers Gold.}{Dark~Ales, Stouts}{Bittering}{}
\hop{33.0}{7.5}{Southern Cross}{12\%}{The aroma is characterized by a heady mix of lemon peel and pine needles layered beneath the clean spiciness. Primarily a bittering hop but has a nice mellow aroma as a late addition hop.}{Australian~Lagers}{Bittering}{NZ}
\hop{37.5}{7.5}{Tradition}{10--13\%}{High-alpha acid Hallertau variety with German characteristics grown to replace Hersbrucker.}{Lagers, Pilsners, Bocks, Wheats, Weizens}{Bittering}{}
\hop{42.0}{7.5}{Yeoman}{9--14\%}{A popular bittering hop in the UK. Similar to Targets. Not too available in the US.}{British~Ales, British~Lagers}{Bittering}{UK}
\hop{1.5}{10.5}{Banner}{9--11\%}{Similar to Aquila and Cluster with good yield.}{American~Lagers}{Bittering, Flavor}{}
\hop{6.0}{10.5}{Centennial}{9--11\%}{Flowers and citrus most evident. A medium aroma with mid-to-high bittering value makes it a dual purpose choice.}{Medium~American~Ales, Dark~American~Ales}{Bittering, Aroma}{US}
\hop{10.5}{10.5}{Citra}{10--11\%}{Very fruity citrus, peach, apricot, passion fruit, grapefruit, lime, melon, gooseberry, lychee fruit, pineapple, mango, papaya and other tropical fruit flavors and aromas.}{Pale~Ales, IPAs}{All Purpose}{}
\hop{15.0}{10.5}{Galena}{10--12\%}{Medium aroma but pleasant hoppiness. Excellent high alpha acid hop with balanced bittering profiles paired with acceptable hop aroma.}{American~Ales, American~Stouts, American~Lagers}{Bittering}{}
\hop{19.5}{10.5}{Green Bullet}{9--11\%}{A high alpha hop with fruity and resiny flavors and floral aromas. Considered a bittering variety typically for lagers, it also carries a solid Styrian characteristic of subtle spiciness.}{Lagers, Irish~Dry~Stouts, Bitters}{Bittering}{NZ}
\hop{24.0}{10.5}{Omega}{9--11\%}{A very new very bitter hop.}{Ales, Stouts, Lagers}{Bittering}{}
\hop{28.5}{10.5}{Phoenix}{10--12\%}{Attractive English aroma (sources say similar to challenger) with high alpha- acid. Use as an aroma hop were reportedly disappointing.}{English~Ales, Porters, Stouts, ESBs, Bitters}{Bittering}{}
\hop{33.0}{10.5}{Sticklebract}{9--11\%}{Noted for its piney, citrus aroma. May give a unique New Zealand twist to English beer styles. Coarse, high-alpha acid variety.}{Ales}{Bittering}{}
\hop{37.5}{10.5}{Super Alpha}{10--12\%}{Slight fresh grassiness beneath a mix of aromas such as pine needles and lemongrass. A very versatile hop in the brew house where it can be used to deliver a very crisp bitter edge on the back pallet and excellent aroma qualities.}{}{All Purpose}{NZ}
\hop{42.0}{10.5}{Target}{10--12\%}{Widely used for high alpha acid content combined with an acceptable aroma. Pleasant English hop aroma, quite intense.}{British~Ales, British~Lagers}{All Purpose}{UK}
\hop{1.5}{13.5}{Amarillo}{8--10\%}{Popular American mid-range alpha acid variety with a unique and distinct aroma. It has a flowery, citrus-like aroma; more orange than grapefruit.}{Pale~Ales, IPAs, Porters}{Bittering, Flavor}{US}
\hop{6.0}{13.5}{Challenger}{7--10\%}{Mild to Moderate aroma, quite spicy. One of the few recognized all-purpose hops combining moderate amounts of alpha acid with a good kettle aroma.}{British~Ales, British~Lagers}{All Purpose}{UK}
\hop{10.5}{13.5}{Comet}{8--11\%}{A rare US hop. Used primarily for their bittering character. Wild American aroma that is objectionable to some brewers, Comet today is no longer grown commercially.}{Ales, Lagers}{Bittering}{US}
\hop{15.0}{13.5}{NZ Hallertau}{8--9\%}{This aroma hop is characterized by woodsy, citrus notes and a clean taste that has staying power. Higher alpha makes it an acceptable bittering hop.}{Organic~Pilsners, Lagers, German~Beers}{Finishing}{NZ}
\hop{19.5}{13.5}{Northdown}{7--10\%}{Mellow English higher alpha-acid hop. Similar to Northern Brewer, but with a better flavor and aroma than domestic Northern Brewer; A clean bittering hop.}{Heavier~Ales, Porters}{Dual Purpose}{UK}
\hop{24.0}{13.5}{Northern Brewer}{7--11\%}{Moderate alpha acids combined with an acceptable aroma profile. Neutral, clean aroma, woody with evergreen and mint overtones.}{English~Ales, ESBs, Bitters, Porters, German~Lagers, Steam~Beers}{All Purpose}{}
\hop{28.5}{13.5}{Pioneer}{8--10\%}{New dwarf variety with clean bitterness and mild English aroma. Unusual pleasant lemon/grapefruit citrus aroma distinctively hoppy.}{English~Ales, ESBs, Bitters}{Dual Purpose}{}
\hop{33.0}{13.5}{Pride of Ringwood}{7--10\%}{Quite pronounced aroma but not unpleasant, citrus-like. At the time of release in 1965 it was the highest alpha hop in the world. closely associated with such famous beers as Foster's Lager.}{British~Ales, Australian~Beers}{All Purpose}{AU}
\hop{37.5}{13.5}{Sladek}{9--10\%}{Hybrid aroma variety of Saaz type with excellent impact on hoppy taste and aroma of beer. New dual purpose Czech hop.}{Lagers}{Finishing}{CZ}
\hop{42.0}{13.5}{Zenith}{9--10\%}{Has a good aroma. Not too available.}{British~Ales, British~Lagers}{Aroma}{}
\hop{1.5}{16.5}{Brewer's Gold}{6--9\%}{Sibling of and similar to Bullion only maturing earlier and more disease resistant. English/wild Canadian cross. Pungent English character.}{Stouts, Dark~Ales}{Bittering}{UK, CA}
\hop{6.0}{16.5}{Bullion}{6.5--9\%}{Intense, black currant aroma, spicy and pungent. One of the earliest high alpha hops in the world. Raised in 1919 in England from a wild Manitoban female crossed with an English male hop.}{Stouts, Dark~Ales}{Bittering}{UK}
\hop{10.5}{16.5}{Cluster}{5.5--8.5\%}{Floral aroma, excellent general-purpose hop with medium and well-balanced bittering potential and no undesirable aroma properties. Good for Dark beers.}{American~Lagers}{All Purpose}{}
\hop{15.0}{16.5}{First Gold}{6--9\%}{Pleasant citrus/apricot nose that is outstanding in ESBs, IPAs, or fruit beers. Dwarf hop with fine English Golding character with higher alpha.}{English~Ales, Porters, ESBs, Fruit~Beers}{All Purpose}{UK}
\hop{19.5}{16.5}{Motueka}{6.5--7.5\%}{A unique aroma and flavor; excellent when employed in multiple additions from a single hop bill and sits well on the palate to balance speciality malt sweetness.}{Lagers, Belgian~Ales, Cask~Bitters, Bohemian~Pilsners}{All Purpose}{NZ}
\hop{24.0}{16.5}{Orion}{6--8\%}{Classic Noble style, dual-use hop from Germany.}{German~Ales, German~Lagers}{Finishing, Flavor}{}
\hop{28.5}{16.5}{Palisade}{6--9\%}{Aroma described as floral, Subtle Apricot, Grassy or ``Pretty.'' Non-aggressive, smooth hop flavor with a fruity, non-citrus aroma more characteristic of English style Pale ales.}{English~Ales}{Finishing}{}
\hop{33.0}{16.5}{Perle}{7--9\%}{A palate-pleaser with its moderate, pleasant, minty clean bittering qualities and refreshing, spicy ``green hop'' aroma. Derived from English Northern Brewer.}{Pale~Ales, Lagers, Stouts}{All Purpose}{}
\hop{37.5}{16.5}{Sterling}{6--9\%}{Herbs and spices dominate, flowers and citrus around the fringes. Moderate bittering values with a mix of Saaz and Mt. Hood properties.}{Ales, Pilsners, Lagers}{Aroma}{}
\hop{42.0}{16.5}{Talisman}{7--9\%}{An improved Cluster variety. Not much more info available.}{}{All Purpose}{}
\hop{1.5}{19.5}{Aquila}{6--7.5\%}{Recently developed as an aroma hop originating in the US.}{American~Ales}{Finishing}{US}
\hop{6.0}{19.5}{Bramling Cross}{5--8\%}{Variety Bramling crossed with a male seedling from a Manitoba female. Blackcurrant, lemony aroma.}{Spiced~Ales}{All Purpose}{}
\hop{10.5}{19.5}{Cascade}{4--7\%}{Flowery, citrus, and spice with grapefruit the noticeable fragrance quite often. This medium aroma balances the low bittering value. Good for flavor and aroma, but an acceptable bittering hop.}{Pale~Ales, IPAs, Porters}{All Purpose}{}
\hop{15.0}{19.5}{Delta}{6.5\%}{Aroma Type Hop Mild and pleasant, slightly spicy with a hint of citrus. Still experimental.}{American~Pale~Ales, American~IPAs}{Dual Purpose}{}
\hop{19.5}{19.5}{Domestic Hallertau}{5--6\%}{This is a noble aroma hop with subtle flower and spice fragrances defining its ``\"{u}ber alles'' superiority.}{Stock~Ales, Altbiers, Belgian~Ales, Pilsners, Bocks, Lagers, Wheats}{Finishing}{DE}
\hop{24.0}{19.5}{Glacier}{5--6\%}{Pleasant aroma of citrus mixed with sweet fruity of pear or apricot. Aroma seems to be the strong suit of this hop.}{American~Ales, ESBs}{Finishing}{}
\hop{28.5}{19.5}{Mt.\ Hood}{5--8\%}{Hybrid of Hallertau with similar mild flower/spice aroma characteristics with a hint more of the forest. ``Clean'' commonly describes it.}{American~Ales, American~Lagers, German~Ales, German~Lagers}{Finishing}{}
\hop{33.0}{19.5}{Pacifica}{5--6\%}{A blend of new and old-world tastes; orange marmalade aptly describes the citrus aroma notes achieved through late addition. Bittering quality is such that early additions net a soft yet solid finish even in highly bittered beers.}{}{Finishing, Aroma}{NZ}
\hop{37.5}{19.5}{Progress}{5--8\%}{Similar to Fuggles but a little sweeter. Bred from Whitbred Goldings vareity but with an assertive fruity aroma. Robust, fruity, with lime; described as ``junipery.''}{Cask~Ales, English~Ales, Scottish~Ales}{Dual Purpose}{}
\hop{42.0}{19.5}{Santiam}{5.5--8\%}{Resembles a Noble hop aroma. Herbal. Floral. This is a mixture of Tettnanger, Mittelfr\"{u}h, Cascades, and others. Aroma is a suggestion of Tettnanger.}{American~Lagers, German~Lagers, German~Ales, Wheats}{Finishing}{US}
\hop{1.5}{22.5}{Anthanum}{3.5--6\%}{This hop is used for its aromatic properties and moderate bittering. It has aromas that are citrus (Grapefruit), earthy, and floral.}{American~Ales}{Finishing}{US}
\hop{6.0}{22.5}{Fuggle}{4--5.5\%}{Classic English aroma hop with moderate bittering value. Mild and pleasant, spicy, soft, woody, with some fruit tones. Also known over-seas as Styrian Golding.}{English~Ales, Pale~Ales, Porters, Stouts}{Finishing}{UK}
\hop{10.5}{22.5}{Golding}{4--5\%}{Refined Gentle, Fragrant and pleasant with flowery tones, that has produced some of England's best bitters.}{English~Ales, Belgian~Ales}{Finishing}{UK}
\hop{15.0}{22.5}{Huller}{4--6\%}{A universal hop for both bittering and aroma.}{German~Ales, German~Lagers}{Bittering, Aroma}{}
\hop{19.5}{22.5}{Riwaka}{4.5--6.5\%}{Powerful grapefruit ``citrus'' characters are literally breathtaking. A punchy addition to the new-world styles of Pale Ale and regional Pilsners. A cult hero that is established in the NZ craft beer culture.}{Pale~Ales}{Finishing}{NZ}
\hop{24.0}{22.5}{Spalter}{3--6\%}{Traditional German noble hop. A Saaz alternative, aromatic and flavorful.}{German~Lagers}{Finishing}{DE}
\hop{28.5}{22.5}{Styrian Goldings}{4--6\%}{Delicate, slightly spicy, soft and floral. A world renowned aroma hop with widespread usage in both ale and lager brewing. Grown in Slovenia.}{English~Ales, Oktoberfest~Lagers, Belgian~Ales, Pilsners}{Finishing}{SI}
\hop{33.0}{22.5}{Tettnang}{4--5\%}{Fine, very spicy, mild, floral, very aromatic. Recently established in the US, a traditional German variety, true noble aroma variety.}{Wheats, Lagers}{Finishing}{DE, US}
\hop{37.5}{22.5}{Vanguard}{4--6\%}{Slightly flowery, mild. Similar to Hallertau Mittlefr\"{u}h and saaz in aroma. A gentle hop for subtle bitterness, aroma, and flavor.}{Light~Lagers, Pilsners, K\"{o}lsch, Wheat, Munich~Helles}{Finishing}{}
\hop{42.0}{22.5}{Willamette}{4--6\%}{The king of aroma hops in the US with its modest bittering value and the joyous harmony of flowers, fruit, earth and spice. A quality aroma hop with a smooth soft flavor.}{American/British~Ales~and~Lagers}{Finishing}{}
\hop{1.5}{25.5}{Crystal}{3--5\%}{Mild and pleasant, a delicate blend of spices and flowers. Low bittering value adds to the charm.}{German-style~Pilsners, Lagers, K\"{o}lsch, ESB, Belgian~Ales}{Finishing}{}
\hop{6.0}{25.5}{German Hallertau}{3.5--5\%}{Traditionally a superior German aroma hop. Mild to semi-strong aroma, the most popular variety. Excellent flavor.}{Wheats, Altbiers, Pilsners, Belgian~Ales, Lagers}{Finishing}{DE}
\hop{10.5}{25.5}{Hersbrucker Hallertau}{3--5\%}{Drier, spicier than Hallertauer. Most important aroma variety in Germany.}{German~Ales, German~Lagers}{Finishing}{DE}
\hop{15.0}{25.5}{Kent Golding}{3--5\%}{Gentle, fragrant, and pleasant with flowery tones. Referred to as ``East Kent Goldings'' if grown in East Kent, ``Kent Goldings'' if grown in Mid-Kent, and ``Goldings'' if grown elsewhere.}{English~Ales, Belgian~Ales}{Finishing}{UK}
\hop{19.5}{25.5}{Liberty}{3--5\%}{American cousin to Hallertau with very similar flower and spice characteristics, mild and pleasant, quite fine. Best used as a finishing hop in German-style lagers.}{American~Ales, German~Ales, Lagers, Pilsners, Bocks, K\"{o}lsch}{Finishing}{US}
\hop{24.0}{25.5}{Lublin}{3--4.5\%}{Mild and typical of noble aroma types. Another source of the classical noble- aroma type hop with long and strong traditions. Widely believed to be a clone of Saaz.}{}{Finishing}{PL}
\hop{28.5}{25.5}{Mittelfr\"{u}h Hallertau}{3--5\%}{Typical characteristics of a Hallertau; mild and pleasant aroma.}{Stock~Ales, Altbiers, Belgian~Ales, Continental~Lagers, Pilsners, Bocks, Lagers, Wheats}{Aroma}{DE}
\hop{33.0}{25.5}{Saaz}{3--5\%}{The Old World steadfast standby made famous by Pilsner Urquell possesses the aromatic blend of earth and spice notable in European nobles. Low bittering value.}{Continental~Lagers, Wheats, Pilsners, Lagers}{Finishing}{CZ}
\hop{37.5}{25.5}{Saphir}{3--4.5\%}{Refined, sweet, mild clean citrus, hint of tangerine. It was bred with a Hallertau parent and probably a long list of other hops to make it more commercially viable.}{Pilsners, German~Lagers, Belgian~Whites}{Finishing}{}
\hop{42.0}{25.5}{Ultra}{3\%}{Newer domestic aroma variety with Saaz characteristics. Very fine, mild, spicy with floral notes. Bred as a substitute for Hallertauer Mittelfr\"{u}h.}{Pilsners, German~Lagers}{Finishing}{}